|

### 2021-03-17 appendix/appendix.Rmd
embedding multilevel structure dataset

# Estimation of the 
estim_het <- function(dat, yi, v, random, slab, hetvar = NULL) {
  if (is.null(hetvar)) {
    print('Hetvar should be different than null.')
    break
  }
  levshetvar <- unique(hetvar)
  fullmod <- rma.mv(yi = yi, V = v, random = random,
                    data = dat, slab = slab, method = 'REML',
                    test = 't', tdist = T)
  res <- tibble()
  for (i in levshetvar) {
    partmod <- rma.mv(yi = yi, V = v, 
                      random = random,
                      data = dat, slab = slab, 
                      method = 'REML',
                      test = 't', tdist = T, 
                      subset = hetvar == i)
    partmod <- broom_mod(partmod, subgroup = T)
    partmod$byvar = i
    partmod <- bind_rows(
      tibble(TE = NA, seTE = NA,
             studlab = toupper(i), lower = NA,
             upper = NA, group = "B", byvar = i),
      partmod
    )
    res <- bind_rows(res, partmod)
  }
  aux <- data.frame(predict(fullmod))
  res <- bind_rows(res,
                   tibble(
                     byvar = NA,
                     TE = c(aux$pred, NA),
                     seTE = c(aux$se, NA),
                     studlab = c("Overall Effect", "Prediction Interval"),
                     lower = c(aux$ci.lb, aux$cr.lb),
                     upper = c(aux$ci.ub, aux$cr.ub),
                     group = "B"))
  res <- data.frame(res)
  res$byvar <- toupper(res$byvar)
  return(res)
}

@@

We webscraped three large academic databases: \href{https://scholar.google.com/}{Google Scholar} (n = 1001); \href{https://academic.microsoft.com/home}{Microsoft Academic} (n = 927); and \href{https://www.scopus.com/}{Scopus} (n = 736). The `R` script we wrote extracted the article title, abstract, authors, year, journal of publication, and database from which the record originated. Our code is available in section \ref{sub:scrap} below. We screened these results with an English language and article restriction, that is, we excluded all records written in other languages and all that were not academic papers, such as book chapters or doctoral theses. We set no restriction to unpublished articles.

@@

```{r, fig.width=4, fig.height=3, fig.cap="Dependent variables across the law of 1/n studies", size="footnotesize", cache=TRUE, echo = FALSE}
dat %>%
  select(id, depvar2) %>%
  unique() %>%
  mutate(depvar2 = factor(depvar2,
                          labels = c("Per Capita Expenditure",
                                     "Percentage GDP Government Expenditure",
                                     "Log Per Capita Expenditure"))) %>%
  ggplot(aes(x = depvar2)) +
    geom_bar(color = "black") +
  labs(x = "Dependent Variables",
       y = "") +
  coord_flip() +
  theme_bw()
```

@@

```{r, fig.width=4, fig.height=3, fig.cap="Independent variables across the law of 1/n studies", size="footnotesize", echo = FALSE, cache=TRUE}
dat %>%
  select(id, indepvar2) %>%
  unique() %>%
  mutate(indepvar2 = factor(indepvar2, labels = c("K (upper house legislators)",
                                                  "N (lower house legislators)",
                                                  "Log N"))) %>%
  ggplot(aes(x = indepvar2)) +
    geom_bar(color = "black") +
  labs(x = "Independent Variables",
       y = "") +
  coord_flip() +
  theme_bw()
```

@@

```{r, size="footnotesize", cache=TRUE, fig.width=5, fig.height=4, echo = FALSE}
dat %>%
  ggplot(aes(x = coef)) +
  geom_histogram(bins = 15, color = "black") +
  labs(x = "Coefficients") +
  theme_bw()
```

@@

```{r, size="footnotesize", cache=TRUE, fig.width=5, fig.height=4, echo = FALSE}
dat %>%
  ggplot(aes(x = SE)) +
  geom_histogram(bins = 10, color = "black") +
  labs(x = "Standard Errors") +
  theme_bw()
```

>>>>

# Estimation of the 
estim_het <- function(dat, yi, v, random, slab, hetvar = NULL) {
  if (is.null(hetvar)) {
    stop('Hetvar should be different than null.')
  }
  levshetvar <- unique(hetvar)
  fullmod <- rma.mv(yi = yi, V = v, random = random,
                    data = dat, slab = slab, method = 'REML',
                    test = 't', tdist = T)
  res <- tibble()
  for (i in levshetvar) {
    partmod <- rma.mv(yi = yi, V = v, 
                      random = random,
                      data = dat, slab = slab, 
                      method = 'REML',
                      test = 't', tdist = T, 
                      subset = hetvar == i)
    partmod <- broom_mod(partmod, subgroup = T)
    partmod$byvar = i
    partmod <- bind_rows(
      tibble(TE = NA, seTE = NA,
             studlab = toupper(i), lower = NA,
             upper = NA, group = "B", byvar = i),
      partmod
    )
    res <- bind_rows(res, partmod)
  }
  aux <- data.frame(predict(fullmod))
  res <- bind_rows(res,
                   tibble(
                     byvar = NA,
                     TE = c(aux$pred, NA),
                     seTE = c(aux$se, NA),
                     studlab = c("Overall Effect", "Prediction Interval"),
                     lower = c(aux$ci.lb, aux$cr.lb),
                     upper = c(aux$ci.ub, aux$cr.ub),
                     group = "B"))
  res <- data.frame(res)
  res$byvar <- toupper(res$byvar)
  return(res)
}

@@

We webscraped three large academic databases: \href{https://scholar.google.com/}{Google Scholar} (n = 1001); \href{https://academic.microsoft.com/home}{Microsoft Academic} (n = 927); and \href{https://www.scopus.com/}{Scopus} (n = 736). The `R` script we wrote extracted the article title, abstract, authors, year, journal of publication, and database from which the record originated. Our code is available in section \ref{sub:scrap} below. We screened these results with an English language and article restriction, that is, we excluded all records written in other languages and all that were not academic papers, such as book chapters or doctoral theses. We set no restriction to unpublished articles. XXXX CATARINA AND HUZEYFE: FIX THIS

@@

```{r, fig.width=4, fig.height=3, fig.cap="Dependent variables across the law of 1/n studies", size="footnotesize", cache=TRUE, echo = FALSE}
dat %>%
  select(id, depvar2) %>%
  unique() %>%
  mutate(depvar2 = factor(depvar2,
                          labels = c("Per Capita Expenditure",
                                     "Percentage GDP Government Expenditure",
                                     "Log Per Capita Expenditure"))) %>%
  ggplot(aes(x = depvar2)) +
    geom_bar(color = "black") +
  labs(x = "",
       y = "Dependent Variables") +
  coord_flip() +
  theme_bw()
```

@@

```{r, fig.width=4, fig.height=3, fig.cap="Independent variables across the law of 1/n studies", size="footnotesize", echo = FALSE, cache=TRUE}
dat %>%
  select(id, indepvar2) %>%
  unique() %>%
  mutate(indepvar2 = factor(indepvar2, labels = c("K (upper house legislators)",
                                                  "N (lower house legislators)",
                                                  "Log N"))) %>%
  ggplot(aes(x = indepvar2)) +
    geom_bar(color = "black") +
  labs(x = "",
       y = "Independent Variables") +
  coord_flip() +
  theme_bw()
```

@@

```{r, size="footnotesize", cache=TRUE, fig.width=5, fig.height=4, echo = FALSE}
dat %>%
  ggplot(aes(x = coef)) +
  geom_histogram(bins = 15, color = "black") +
  labs(x = "Coefficients", y = '') +
  theme_bw()
```

@@

```{r, size="footnotesize", cache=TRUE, fig.width=5, fig.height=4, echo = FALSE}
dat %>%
  ggplot(aes(x = SE)) +
  geom_histogram(bins = 10, color = "black") +
  labs(x = "Standard Errors", y = '') +
  theme_bw()
```
